Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-04 paper.tex
Modified iRail API feature section.

The iRail API is a XML/JSON HTTP API where each request on \url{http://api.irail.be} returns a response that can be used directly in an end-user app.
It contains four features: a route planning query (\url{http://api.irail.be/connections/{?from,to,date,time}}), a query for the next departures in a certain station (\url{http://api.irail.be/liveboard/{?station,date,time}}), a query for the status of a certain train (\url{http://api.irail.be/vehicle/{?id,date}}) and a query for a list of all stations (\url{http://api.irail.be/stations/}).
We have gathered the \emph{Apache} \emph{access.log} files generated between 2012 and 2015 containing: 
\begin{itemize}
  \item Timestamp,
  \item HTTP Status Code,
  \item Request Path (e.g., \url{/connections/?from=Ghent\&to=Antwerp})
  \item User-Agent (cfr. RFC2616\footnote{The User-Agent request-header field contains information about the user agent originating the request. This is for statistical purposes, the tracing of protocol violations, and automated recognition of user agents for the sake of tailoring responses to avoid particular user agent limitations -- \url{http://www.w3.org/Protocols/rfc2616/rfc2616-sec14.html}})
\end{itemize}

@@

>>>>

The iRail API is a XML/JSON HTTP API where each request on \url{http://api.irail.be} returns a response that can be used directly in an end-user app.
It contains four features: 
\begin{itemize}
\item Route Planning Feature (\url{http://api.irail.be/connections/{?from,to,date,time}}).
\item Next Departures Feature (\url{http://api.irail.be/liveboard/{?station,date,time}}).
\item Train Status Feature query (\url{http://api.irail.be/vehicle/{?id,date}}).
\item List All Stations Feature (\url{http://api.irail.be/stations/}).
\end{itemize}

\todo{what are the intended functions of each feature? We should mention that the route planning feature is perhaps the most popular among lay users? Thus is also has good potential to be used as a proxy for analysis...}

@@

We have gathered the \emph{Apache} \emph{access.log} files generated between 2012 and 2015 containing: 
\begin{itemize}
  \item Timestamp,
  \item HTTP Status Code,
  \item Request Path (e.g., \url{/connections/?from=Ghent\&to=Antwerp})
  \item User-Agent (cfr. RFC2616\footnote{The User-Agent request-header field contains information about the user agent originating the request. This is for statistical purposes, the tracing of protocol violations, and automated recognition of user agents for the sake of tailoring responses to avoid particular user agent limitations -- \url{http://www.w3.org/Protocols/rfc2616/rfc2616-sec14.html}})
\end{itemize}
